Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-31 TACAS2018/paper.tex
wording

In embedded software programs interacting and/or simulating physical plants
it is of great importance to understand the effects of the chosen numeric
representation for the continuous state-space.  These representations are
almost invariably approximations to the original which are assumed to be
precise enough as to not cause any trouble, but it is precisely this
assumption that often results in the most difficult and dangerous errors. 
There are generally speaking two paradigms for representing numbers in
programs: fixed and variable precision numbers.  We~refer to both of these
as finite word length representations (FWL).  In fact, these subdivide into
multiple data types such as integer bit-vectors, fixed or floating point
numbers and rationals).  In this section we will be discussing fixed and
floating point numbers.  On one hand, we have variable word length types
which will attempt to use as much memory as needed to precisely represent
the original domain (usually the reals).  In this case the limitations are
caused by memory and speed, both of which are directly affected by the
increasingly larger word lengths.  Multiple Precision Floating Point
Arithmetic and Software Rationals are good examples of these cases.  It is
possible for some of these data types to have memory constraints, at which
point they fall into the second category.  Fixed precision data types are
most common in software programs.  Whether they be Floating Point or Fixed
Point (of which integers are the special case for 0 decimal places) numbers,
the problem arises in the misrepresentation of the reals (or equivalent data
type being represented).  Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed
point domain with $M$ bits representing the binary word length of the
representation and $F$ bits representing the pre-scaling $2^{-F}$
(\emph{i.e} the number of bits after the decimal place).  We note that a
negative $F$ denotes an integer multiplication that adds $-F$ trailing zeros
in the number represented by~$M$.

@@

%Let us first consider the effect of the quantization errors. 
%Within the controller, state values are manipulated at low precision.
%Furthermore, the quantizers for the DAC and the ADC introduce truncation errors
%which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
%and $\mathcal{F}_{\langle A \rangle}$, respectively. Finally, let us call $\vec{\nu}_e$ the
%error caused by the FWL effects on the observer
%\todo{the observer was not defined..}
%(\emph{i.e} the numerical errors 
%in the calculations as opposed to the estimation error).
%The inputs are computed using the following equation: 
%%
%\begin{align}
%u_{k}&=\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right)
%\label{eq:uk}
%\end{align}
%
%This induces two types of the errors: first, the truncation
%error due to the domain transformations $\mathcal{F}_{\langle *
%\rangle}(\cdot)$; and second, the rounding error introduced by the
%multiplication operation.  We represent these errors as non-deterministic
%additive noise.

>>>>

In embedded software programs interacting and/or simulating physical plants
it is of great importance to understand the effects of the chosen numeric
representation for the continuous state-space.  These representations are
almost invariably approximations to the original which are assumed to be
precise enough as to not cause any trouble, but it is precisely this
assumption that often results in the most difficult and dangerous errors. 
There are generally speaking two paradigms for representing numbers in
programs: fixed and variable precision numbers.  We~refer to both of these
as finite word length representations (FWL).  They subdivide into a variety
of data types such as integer bit-vectors, fixed or floating point numbers
and rationals).  In this section we will be discussing fixed and floating
point numbers.

On one hand, we have variable word length types, which will use as much
memory as needed to precisely represent the original domain (usually the
reals).  In this case, the limitations are caused by memory and speed, both
of which are directly affected by the increasingly larger word lengths. 
Multiple Precision Floating Point Arithmetic and Software Rationals are good
examples of these cases.  It is possible for some of these data types to
have memory constraints, at which point they fall into the second category. 
Fixed precision data types are most common in software programs.  Whether
they be Floating Point or Fixed Point (of which integers are the special
case for 0 decimal places) numbers, the problem arises in the
misrepresentation of the reals (or equivalent data type being represented). 
Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed point domain with $M$ bits
representing the binary word length of the representation and $F$ bits
representing the pre-scaling $2^{-F}$ (i.e., the number of bits after
the decimal place).  We note that a negative $F$ denotes an integer
multiplication that adds $-F$ trailing zeros in the number represented
by~$M$.

@@

%Let us first consider the effect of the quantization errors. 
%Within the controller, state values are manipulated at low precision.
%Furthermore, the quantizers for the DAC and the ADC introduce truncation errors
%which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
%and $\mathcal{F}_{\langle A \rangle}$, respectively. Finally, let us call $\vec{\nu}_e$ the
%error caused by the FWL effects on the observer
%\todo{the observer was not defined..}
%(i.e., the numerical errors 
%in the calculations as opposed to the estimation error).
%The inputs are computed using the following equation: 
%%
%\begin{align}
%u_{k}&=\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right)
%\label{eq:uk}
%\end{align}
%
%This induces two types of the errors: first, the truncation
%error due to the domain transformations $\mathcal{F}_{\langle *
%\rangle}(\cdot)$; and second, the rounding error introduced by the
%multiplication operation.  We represent these errors as non-deterministic
%additive noise.
